{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-24 thesis/quicksand.tex
two tiny tweaks

Quicksand is an independent program that wraps the execution of several stateless model checker instances.
It is expected that Landslide be this checker,
but any other tool which implements the same messaging interface would be compatible as well.
The implementation is roughly 3000 lines of C.
All source files mentioned in this section live in the {\tt id/} subdirectory of the Landslide repository,
with the exception of the Landslide extensions listed last.
As \Cref{chap:landslide} was in some sense a developer's guide to Landslide,
this section will serve similarly for Quicksand.

>>>>

Quicksand is an independent program that wraps the execution of several stateless model checker instances.
It is expected that Landslide be this checker,
but any other tool which implements the same messaging interface would be compatible as well.
The implementation is roughly 3000 lines of C.
All source files mentioned in this section live in the {\tt id/} subdirectory of the Landslide repository,
with the exception of the Landslide extensions (listed last).
As \Cref{chap:landslide} was in some sense a developer's guide to Landslide,
this section will serve similarly for Quicksand.

### 2018-12-24 thesis/thesis.tex
upd change bar config for qs
shearbox the star in madoka magica
quicksand write intro and about pps
add inco, birb lite fonts; sigbovik easter egg; fix the issue where numbers in urls show up in charter instead of monospace
two tiny tweaks

%\usepackage{fontspec}
\usepackage{mathspec}
\usepackage{xeCJK}
\usepackage[xetex]{xechangebar}

@@

\setCJKmainfont{HeiseiMinStd-W5}[Path = ./fonts/]
%\newfontfamily\arabicfont{Droid Sans Arabic} % doesn't respond to Script = Arabic :(
%\newfontfamily\arabicfont{LateefGR-Regular}[Path = ./fonts/] % doesn't respond to Script = Arabic :(
\newfontfamily\arabicfont{Amiri-Regular}[Path = ./fonts/, Script = Arabic]

@@

%\newcommand\revision[1]{#1\xspace}
\newcommand\revision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
%\newcommand\revisionminor[1]{#1\xspace}
\newcommand\revisionminor[1]{\cbstart{}#1\cbend\xspace}

@@

\newcommand\simics{\textsc{Simics}}
\newcommand{\sect}[1]{\S #1}
\newcommand\hilight[2]{\color{#1}#2\color{black}}
\definecolor{orange}{RGB}{192,96,0}
\definecolor{olivegreen}{RGB}{0,127,0}
\definecolor{brickred}{RGB}{192,0,0}
\definecolor{commentblue}{RGB}{0,0,192}
% colors from sigbovik for tsx/etc
% threads
\definecolor{lavender}{RGB}{102,65,208} % (?? i don't know what happened here anymore but it looks good)
\definecolor{seafoam}{RGB}{56,158,68} % * 2/3
\definecolor{salmon}{RGB}{208,89,74} % * 7/8
\definecolor{goldish}{RGB}{128,96,32}
% eval data
\definecolor{darkcyan}{RGB}{0,128,128}
\definecolor{lime}{RGB}{48,128,0}
\definecolor{darklavender}{RGB}{68,44,138}
\definecolor{brownish}{RGB}{128,96,0}
\definecolor{pinkish}{RGB}{128,34,102} % ff4488
% syntax hilighting
\newcommand\flow[1]{\hilight{brownish}{#1}\xspace}
\newcommand\const[1]{\hilight{brickred}{#1}\xspace}
\newcommand\call[1]{\hilight{pinkish}{#1}}
\newcommand\ctype[1]{\hilight{lime}{#1}\xspace}
\newcommand\ccomment[1]{\hilight{darkcyan}{#1}\xspace}

@@

Concurrency testing is, in a way, a microcosm for research in general:
an exponentially large problem
that invariably thwarts they whoever try to solve it ``perfectly'';
it bears fruit only to one who can find their own human-oriented meaning in partial results and compromises.
I speak of course literally on one side of this analogy, figuratively on the other.
This thesis has demonstrated such meaning for stateless model checking,
choosing perhaps one of the most challenging demographics of programmers in need of concurrency testing,
the undergraduate operating systems student,
as its target audience,
\revision{ultimately helping 73\% of participating students to find bugs in their code,
56\% to fix any such bugs,
and 34\% to fix all such bugs,
before their project deadline.}
Along the way, I justified \revisionminor{Landslide's} applicability to problems beyond CMU's walls as well
by showing positive results at other universities,
and by addressing a new concurrency model developed by \revisionminor{the hardware} industry in just the last decade.
% also by comparing the preemption bounds of quicksand eval's bugs to prior work in ICB
% and finding them to actually be skewed to DEEPER bugs than in the "real" "world", so take that
As I write this I am also collaborating with 15-410 staff
to integrate Landslide as an official part of the course grading infrastructure,
so in some sense the na\"{i}ve wish to make an ``automatic TA'' that drew my attention to grad school to begin with
has also been fulfilled.

>>>>

%\usepackage{fontspec}
\usepackage{mathspec}
\usepackage{xeCJK}
\usepackage[xetex]{xechangebar}
\usepackage[nomessages]{fp} % for xshearbox, see quicksand.tex

@@

\setCJKmainfont{HeiseiMinStd-W5}[Path = ./fonts/]
%\newfontfamily\arabicfont{Droid Sans Arabic} % doesn't respond to Script = Arabic :(
%\newfontfamily\arabicfont{LateefGR-Regular}[Path = ./fonts/] % doesn't respond to Script = Arabic :(
\newfontfamily\arabicfont{Amiri-Regular}[Path = ./fonts/, Script = Arabic]
\setmonofont{Inconsolata-Regular}[Path = ./fonts/]
\newfontfamily\birbaslo{BirbasloText}[Path = ./fonts/]

% https://tex.stackexchange.com/questions/99770/problem-with-digits-in-urls-when-using-mathspec-and-hyperref/99774#99774
% make numbers render in monospace in urls, while render in main font in math mode
\makeatletter
     \DeclareMathSymbol{0}{\mathalpha}{\eu@DigitsArabic@symfont}{`0}
     \DeclareMathSymbol{1}{\mathalpha}{\eu@DigitsArabic@symfont}{`1}
     \DeclareMathSymbol{2}{\mathalpha}{\eu@DigitsArabic@symfont}{`2}
     \DeclareMathSymbol{3}{\mathalpha}{\eu@DigitsArabic@symfont}{`3}
     \DeclareMathSymbol{4}{\mathalpha}{\eu@DigitsArabic@symfont}{`4}
     \DeclareMathSymbol{5}{\mathalpha}{\eu@DigitsArabic@symfont}{`5}
     \DeclareMathSymbol{6}{\mathalpha}{\eu@DigitsArabic@symfont}{`6}
     \DeclareMathSymbol{7}{\mathalpha}{\eu@DigitsArabic@symfont}{`7}
     \DeclareMathSymbol{8}{\mathalpha}{\eu@DigitsArabic@symfont}{`8}
     \DeclareMathSymbol{9}{\mathalpha}{\eu@DigitsArabic@symfont}{`9}
\makeatother

@@

\newcommand\revision[1]{#1\xspace}
%\newcommand\revision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
\newcommand\revisionminor[1]{#1\xspace}
%\newcommand\revisionminor[1]{\cbstart{}#1\cbend\xspace}
% quicksand chapter revisions only
\newcommand\qrevision[1]{\cbstart[0.5em]{}#1\cbend\xspace}
\newcommand\qrevisionminor[1]{\cbstart{}#1\cbend\xspace}

@@

\newcommand\simics{\textsc{Simics}}
\newcommand{\sect}[1]{\S #1}
\newcommand\hilight[2]{\color{#1}#2\color{black}}
\definecolor{orange}{RGB}{192,96,0}
\definecolor{olivegreen}{RGB}{0,127,0}
\definecolor{brickred}{RGB}{192,0,0}
\definecolor{commentblue}{RGB}{0,0,192}
% colors copied back from snake fight for quicksand example codez
\definecolor{darkorange}{RGB}{192,128,0}
\definecolor{darkblue}{RGB}{0,97,192}
\definecolor{assertfail}{RGB}{224,0,56} % was 'pinkish' in snakefight
% colors from sigbovik for tsx/etc
% threads
\definecolor{lavender}{RGB}{102,65,208} % (?? i don't know what happened here anymore but it looks good)
\definecolor{seafoam}{RGB}{56,158,68} % * 2/3
\definecolor{salmon}{RGB}{208,89,74} % * 7/8
\definecolor{goldish}{RGB}{128,96,32}
% eval data
\definecolor{darkcyan}{RGB}{0,128,128}
\definecolor{lime}{RGB}{48,128,0}
\definecolor{darklavender}{RGB}{68,44,138}
\definecolor{brownish}{RGB}{128,96,0}
\definecolor{pinkish}{RGB}{128,34,102} % ff4488
% syntax hilighting
\newcommand\flow[1]{\hilight{brownish}{#1}\xspace}
\newcommand\const[1]{\hilight{brickred}{#1}\xspace}
\newcommand\call[1]{\hilight{pinkish}{#1}}
\newcommand\ctype[1]{\hilight{lime}{#1}\xspace}
\newcommand\ccomment[1]{\hilight{darkcyan}{#1}\xspace}

@@

Concurrency testing is, in a way, a microcosm for research in general:
an exponentially large problem
that invariably thwarts they whoever try to solve it ``perfectly'';
it bears fruit only to one who can find their own human-oriented meaning in partial results and compromises.
I speak of course literally on one side of this analogy, figuratively on the other.
This thesis has demonstrated such meaning for stateless model checking,
choosing perhaps one of the most challenging demographics of programmers in need of concurrency testing,
the undergraduate operating systems student,
as its target audience,
\revision{ultimately helping 73\% of participating students to find bugs in their code,
56\% to fix any such bugs,
and 34\% to fix all such bugs,
before their project deadlines.}
Along the way, I justified \revisionminor{Landslide's} applicability to problems beyond CMU's walls as well
by showing positive results at other universities,
and by addressing a new concurrency model developed by \revisionminor{the hardware} industry in just the last decade.
% also by comparing the preemption bounds of quicksand eval's bugs to prior work in ICB
% and finding them to actually be skewed to DEEPER bugs than in the "real" "world", so take that
As I write this I am also collaborating with 15-410 staff
to integrate Landslide as an official part of the course grading infrastructure,
so in some sense the na\"{i}ve wish to make an ``automatic TA'' that drew my attention to grad school to begin with
has also been fulfilled.
